Discovering cell type motifs in connectomics data

### 2013-12-26 docs/paper.tex
added fixed gibbs
updates to mouse pipeline to plot

\subsection{Other Likelihoods}
\label{supp:otherlikelihoods}
 - Reparameterized logistic-distance bernoulli with fixed lambda

 - Logistic-distance poisson

@@

\FloatBarrier
\subsection{Comparison to IRM for Mouse Retina}

@@

@@

>>>>

\subsection{Other Likelihoods}
\label{supp:otherlikelihoods}

We reparameterized the Logistic-Distance Bernoulli likelihood to
better capture the microprocessor data structure. We explicitly
setting the maximum probability $p$ of the logistic function on a
per-component basis, drawing from a global $p \sim Beta(\alpha_{hp},
\beta_{hp})$. Then $\lambda$ is set for each component as a global
hyperparameter, $\lambda$.

The ``logistic-distance Poisson'' spatial model assumes that, if cell
$e_i$ is of class $m$ and cell $e_j$ is of class $n$, then $\eta_{mn}
= (\mu_{mn}, r_{mn})$, and the probability of $R(e_i, e_j) = c$ synapses between two cells $e_i$ and $e_j$ is given by:
\begin{eqnarray}
\lambda^* &=& \frac{1.0}{1 + \exp \frac{d(e_i, e_j) - \mu_{mn}}{\lambda}}\\
\lambda & = & \lambda^* \cdot (r_{mn} - r_{min}) + r_{min} \\
R(e_i, e_j) \sim Poi(c | \lambda)
\end{eqnarray}

where $\lambda$ and $r_{min}$ are per-graph parameters. Per-component parameters $\mu_{mn} \sim \exp(\mu | \mu^{hp})$ and $r_{mn} \sim \exp(r_{mn} | r_{scale}^{hp})$.

@@

\FloatBarrier
\subsection{Model Comparison for Mouse Retina}

We compare the clusters found by our model, the traditional infinite
stochastic block model, and a finite stochastic block model with the number
of clusters set to the best-found number from our iSRM model ($k=12$).

We see from fig~\ref{fig:supp:irmspatialcomparemouse} that the spatial
variance of our clusters closely matches the ground truth, while the
other two models find spatially-localized
clusters. Figure~\ref{fig:supp:mousecompareari} shows the ARI of our
clustering, the clustering found by the iSBM,
as well as the result of parametrically varying the traditional stochastic
block model for various values of $k$.

The actual clusterings for iSRM, the iSBM, and $SBM_{k=12}$ are shown
in figures \ref{fig:supp:retinabbclusters},
\ref{fig:supp:retinaldclusters}, and
\ref{fig:supp:retinabbfixedclusters} respectively. Each block is a
cluster, with the true cell type indicated along the x-axis, and the
cell ID written to the left or right.

@@

\begin{figure}[h!]
  \centering 
    \centerline{\includegraphics[width=5in]{mouseretina/ari_vs_cluster.pdf}}
  \caption{}
\label{fig:supp:mousecompareari}
\end{figure}

@@

  \centering 
    \centerline{\includegraphics[width=6.5in]{mouseretina/retina.1.2.bb.0.0.data-fixed_20_12-anneal_slow_fixed_400.truth_latent.pdf}}
  \caption{}
\label{fig:supp:retinabbfixedclusters}
\end{figure}
